New first figure

### 2021-04-26 manuscript/bef_stability/fig1_biomass_network.Rmd
Updates

@@

pca_rotated <- compute_rotated_pca(
  .data = habitat_press[, mask],
  naxis = 2
)
p1 <- my_pca_plot(.data = pca_rotated$rotated,
  xaxis = "RC1", yaxis = "RC2", ctb_thld = .4, 
  label_size = 4, force_pull = 0.01, force = 10,
  seed = 1
)

cow_p1 <- plot_grid(NULL, p1, NULL, ncol = 1, rel_heights = c(.02, 1, .02))
fig1ab <- plot_grid(p_st2, cow_p1, ncol = 2, 
  labels = c("A", "B")
)
save_plot(mypath("manuscript", "bef_stability", "figs/fig1ab.png"), fig1ab,
  nrow = 1, 
  ncol = 2,
  base_height = 4,
  base_width = 4
)
``` 
```{r set-up}
st <- c(first_st$station[5], last_st$station[5]) 
library(viridis)
library(ggsci)
library(RColorBrewer)
display.brewer.pal(n = 8, name = 'Dark2')
display.brewer.pal(n = 8, name = 'Set2')

@@

```{r}
cow_fig1ab <- plot_grid(
  p_st2 + theme(panel.background = element_rect(fill = "white")),
  p1, NULL,
  rel_widths = c(.5, .5, .07),
  ncol = 3,
  labels = c("A", "B", ""))
fig1cd <- plot_grid(fig1c, fig1d, ncol = 2, labels = c("C", "D"))
cow_leg_species <- plot_grid(NULL, leg_species, NULL, nrow = 1, rel_widths = c(.25, .5, .25))
fig1 <- plot_grid(cow_fig1ab, fig1cd, cow_leg_species,
  nrow = 3,
  rel_heights = c(.35, .60,.05),
  align = "h"
)
# ele: single column (82 mm), two-thirds page width (110 mm) or full page width (173 mm)
dev.new(width = 8.2, height = 11.0, units = "cm")
# i3: mod + shift + space

>>>>

```{r}
sp_color <- set_color_species(
  node_list = colnames(metaweb_analysis$metaweb),
  resource_list = metaweb_analysis$resource
)
node_sp <- str_extract(colnames(metaweb_analysis$metaweb), "[A-Z|a-z]*")
sp_color[node_sp]

myload(metaweb_analysis,  dir = mypath("data"))
TL <- NetIndices::TrophInd(metaweb_analysis$metaweb)$TL
PlotWeb(
  TL = TL,
  webTL = metaweb_analysis$metaweb,
  colnode = sp_color[node_sp],
  abund = 1,
  collink="grey70",
  scale_abun = .005
) 
```

@@

pca_rotated <- compute_rotated_pca(
  .data = habitat_press[, mask],
  naxis = 2
)
pca_rotated$rotated$loadings[, 2] <- pca_rotated$rotated$loadings[, 2] * (-1) 
p1 <- my_pca_plot(.data = pca_rotated$rotated,
  xaxis = "RC1", yaxis = "RC2", ctb_thld = .4, 
  label_size = 4, force_pull = 0.01, force = 10,
  seed = 1
)
save_plot(file = mypath("manuscript", "bef_stability", "figs", 
	"my_sweet_rotated_pca_reversed_axis2.pdf"),
    plot = p1,
    base_height = 4.5, base_asp = 1.2#1.618 
    )

cow_p1 <- plot_grid(NULL, p1, NULL, ncol = 1, rel_heights = c(.02, 1, .02))
fig1ab <- plot_grid(p_st2, cow_p1, ncol = 2, 
  labels = c("A", "B")
)
save_plot(mypath("manuscript", "bef_stability", "figs/fig1ab.png"), fig1ab,
  nrow = 1, 
  ncol = 2,
  base_height = 4,
  base_width = 4
)

``` 
```{r set-up}
st <- c(first_st$station[5], last_st$station[5]) 
library(viridis)
library(ggsci)
library(RColorBrewer)
display.brewer.pal(n = 8, name = 'Dark2')
display.brewer.pal(n = 8, name = 'Set2')

@@

```{r}
cow_fig1ab <- plot_grid(
  p_st2 + theme(panel.background = element_rect(fill = "white")),
  p1, NULL,
  rel_widths = c(.5, .5, .07),
  ncol = 3,
  labels = c("A", "B", ""))
fig1cd <- plot_grid(fig1c, fig1d, ncol = 2, labels = c("C", "D"))
cow_leg_species <- plot_grid(NULL, leg_species, NULL, nrow = 1, rel_widths = c(.25, .5, .25))
fig1 <- plot_grid(cow_fig1ab, fig1cd, cow_leg_species,
  nrow = 3,
  rel_heights = c(.35, .60,.05),
  align = "h"
)
# ele: single column (82 mm), two-thirds page width (110 mm) or full page width (173 mm)
dev.new(width = 8.2, height = 11.0, units = "cm")
# i3: mod + shift + space 
png(file = “C://R//SAVEHERE//myplot.jpeg”)
plot(x,y)
dev.off()
